---
title: "Alcohol vs Seat choice"
author: "Galilea Hernandez"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data


## Now add in boxplot

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

From observing the graph, we can see that the back row is more prone to drinking alcohol. However the middle seats have many outliers compared to the front and back seats even if their 50% range of data for alcohol drinkers is low. The front seat. has two outliers but the data stayed in a relativley similar range. 
  
### get fancy  



## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

The most an individual drank in a week from the back row was 55 drinks. We see the front seats had the least number of drinks in a week with an individual only of had 20 drinks. While the middle still had a low max of 35 in comparison with the back row, its evident that the middle and back rows are greater than the front row. If we look at the mean of the data between the rows, we can further qualify the fact that the back row has more drinkers than the front row and middle row with a mean of 9.6 arguably quite high while the front and middle rows had a mean of 1.80, and 3,28 respectivley. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
Our p value shows that the probability of getting these results is 116 out of 10,000. 

```{r}
plot(TukeyHSD(model1))
```

## Conclusions


